
  Designing reliable and highly available distributed applications
  typically requires data to be replicated over geo-distributed
  stores.  But, such architectures force application developers to
  make an undesirable tradeoff between ease of reasoning, possible
  when replicated data is required to be strongly consistent, and
  performance, possible only when such guarantees are weakened.
  Unfortunately, undesirable behaviors may arise under weak
  consistency that can violate application correctness, forcing
  designers to either implement ad-hoc mechanisms to avoid these
  anomalies, or choose to run applications using stronger levels of
  consistency than necessary. The former approach introduces unwanted
  complexity, while the latter sacrifices performance.

  In this paper, we describe a lightweight runtime verification system
  that relieves developers from having to make such tradeoffs.
  Instead, our approach leverages declarative axiomatic specifications
  that reflect the necessary constraints any correct implementation
  must satisfy to guide a runtime consistency enforcement mechanism.
  This mechanism guarantees a \emph{provably optimal} strategy that
  imposes no additional communication or blocking overhead beyond what
  is required to satisfy the specification, allowing distributed
  operations to run in a \emph{provably safe} environment.
  Experimental results show that the performance of our automatically
  derived mechanisms is better than both specialized hand-written
  protocols and common store-offered consistency guarantees, providing
  strong evidence of its practical utility.
