\section{Related Works}
\label{sec:rel_works}

%RDTs
Distributed data structures composed of  operation-based RDTs \cite{rdt,crdt} have been implemented and utilized in
multiple systems \cite{tango,cassandra}. 
These systems are developed without assuming eventual consistency
guarantee and include durability and fault tolerance mechanisms,
different from \tool, that similar to \cite{bolton} separates all liveness
and durability issues from the consistency, leaving the former
completely to the underlying data store.


%coordination
The consistency requirements of replicated data-objects have been
studied in several works \cite{autoc,mahsa,bloom}, where multiple
sufficient conditions and analysis techniques are proposed to detect
potential coordination points in programs to enforce strong consistency. \tool takes another approach
and allows users to declare application-level consistency requirements
from a spectrum of (coordination-free) weak consistency guarantees.



%Consistency on top of EC
Several systems \cite{geofast,petersen,cbs,chapar,bolton,quelea} define
and implement various levels of consistency guarantees in order to
protect applications from anomalies admitted under EC.
\cite{chapar} presents a verified implementation for a causally
consistent store, assuming a system model with \emph{session stickiness}, 
where unlike \tool, operations from a session are always routed to the same
replica. The idea of a causally consistent shimlayer on top of an off-the-shelf
ECDS, is proposed in \cite{bolton} and is utilized in \cite{quelea},
to offer three coarse-grained levels of consistency, namely EC, CC and SC. 
\tool extends the shimlayer in \cite{quelea} by maintaining \emph{multiple}
fine-grained weak consistency levels simultaneously (in addition to SC
and EC). 

% contract language
\tool's contract language is inspired
from \cite{rdt,rdtabs}, but similar to \cite{quelea} is crafted for
consistency specification. Compared to \cite{quelea}, \tool introduces a 
more strictly structured syntax (without losing any generality), 
allowing the classification of consistency  guarantees, which enables a 
generic consistency enforcement method, whereas \cite{quelea} relies on
an SMT solver to \emph{map} the operations, to the weakest
\emph{pre-defined} consistency guarantee that satisfies the given
contract. 









