Here, we present detailed proofs of the theorems of the paper by
first presenting a useful lemma.\\
\rule{\textwidth}{1pt}
\begin{lemma}
For all relations {\footnotesize $R\in$ \relationS{}} and execution steps:
{\footnotesize $
(\E,op_{<s,i>}) \;\xrightarrow{V}\; (\E',\eff)
$}
interpretatin of $R$ under $\E$ and $\E'$ (Simply denoted by $R$ and $R'$) differ only on the single
effect $\eta$,
i.e.  {\footnotesize $\forall a,b\not= \eta \Rightarrow (R'(a,b) \Leftrightarrow
R(a,b))$}.
\label{lemma1}
\end{lemma}
\rule{\textwidth}{0.25pt}
\begin{proof}
We prove $\Rightarrow$, the other direction can be shown
similarly. We have the following goal and hypotheses: 
\begin{fmathpar}
\begin{array}{ll}
H_0: & (\E,op_{<s,i>}) \;\xrightarrow{V}\; (\E',\eff) \\
H_1: & a,b \not= \eta\\ 
H_2: & R' (a,b)\\
G_0: & R (a,b)
\end{array}
\end{fmathpar}
Now by destructing $R$, we get the followings, in the only non-trivial
case:
\begin{fmathpar}
\begin{array}{ll}
H_3: & (\trunc{R};r)' (a,b) \\
G_1: & (\trunc{R};r) (a,b)
\end{array}
\end{fmathpar}
which by rewriting the definition in $H_4$ and $G_1$, we get that $y$ exists s.t.
\begin{fmathpar}
\begin{array}{ll}
H_4: & (\trunc{R})'(a,y)\\
H_5: & r'(y,b) \\
G_2: & \exists x. (\trunc{R})(a,x) \wedge (r)(x,b)
\end{array}
\end{fmathpar}
Now by instantiating $G_2$ with $y$ and by inversion: 
\begin{fmathpar}
\begin{array}{ll}
G_3: & (\trunc{R})(a,y) \\ 
G_4: & r(y,b)
\end{array}
\end{fmathpar}
Now by induction on the length of the relation $R$, $G_3$ is trivially
proved and we are left with the following: 
\begin{fmathpar}
\begin{array}{ll}
H_5: & r'(y,b) \\
G_4: & r (y,b)
\end{array}
\end{fmathpar}
Now by inversion on $H_0$ we get two cases. We show the \rulelabel{lb
exec} case, and the other case can be shown similarly (only difference
is $V$ being replaced by $V'$, which
has no effect on the proof):
\begin{fmathpar}
\begin{array}{ll}
H_7: & \visZ' = \visZ \cup V \times \{\eta\} \\
H_8: & \soZ' \; = \soZ \cup  (\EffSoup_{({\sf
SessID}=s)}\times \{\eta\}) 
\end{array}
\end{fmathpar}
Now, because of $H_1$ (and the fact that $y\not= \eta$) it is easy to get the following from $H_7$ and
$H_8$:
\begin{fmathpar}
\begin{array}{ll}
H_9: & \visZ'(y,b) \Rightarrow \visZ(y,b) \\
H_{10}: & \soZ'(y,b) \Rightarrow \soZ(y,b)
\end{array}
\end{fmathpar}
which directly prove $G_4$, in both cases derived by destructing $r$.
\end{proof}








\subsection{Proof of Theorem \ref{theorem:one}}
\label{app:proof1}
\input{Sections/correctness_proof}

\subsection{Proof of Theorem \ref{theorem:two}}
\label{app:proof2}
\input{Sections/maxvis_proof}

\subsection{Proof of Theorem \ref{theorem:three}}
\label{app:proof3}
\begin{footnotesize}
\vspace{-2mm}\rule{\textwidth}{1pt}\\ \vspace{-4mm} \\
Before proving the theorem, we first present and prove a useful lemma
and then we will present 
a new definition, regarding sets of effects.
\begin{lemma}
Under an execution state E and for a given set $S \subseteq E.A$, if
$S$ is $\psi$-consistent under $E$, then $\forall(x\in S).R_S^{-1}(x)
\subseteq S$ under $E$.
\end{lemma}
\begin{proof}
\begin{fmathpar}
\begin{array}{ll}
H_0: & S is \psi\mathtt{-consistent} \\
G_0: & \forall(x\in S). R_{S}^{-1}(x) \subseteq S \\
\end{array}
\end{fmathpar}
after intros:
\begin{fmathpar}
\begin{array}{ll}
H_1: & x \in S\\
G_1: & R_{S}^{-1}(x) \subseteq S \\
\end{array}
\end{fmathpar}
inversion on $H_0$ gives the following:
\begin{fmathpar}
\begin{array}{ll}
H_2: & \forall (\eta \in S).\forall(a\in E.A). R(a,\eta) \Rightarrow a
\in S \\
\end{array}
\end{fmathpar}
which can be rewritten to:
\begin{fmathpar}
\begin{array}{ll}
H_3: & \forall (\eta \in S). R^{-1}(\eta) \subseteq S\\
\end{array}
\end{fmathpar}
however, since $S\subseteq E.A$ then\footnote{\scriptsize we skip the formal proof
of this claim, however, since the only difference in the definitions of
$R^{-1}$ and $R^{-1}_S$ is the extra requirement about mid-level
effects in the latter, it should be a subset of the former.}:
\begin{fmathpar}
\begin{array}{ll}
H_4: & \forall (a\in E.A).R^{-1}_S(a) \subseteq R^{-1}(a)  \\
\end{array}
\end{fmathpar}
Now we can instantiate $H_3$ and $H_4$ into:
\begin{fmathpar}
\begin{array}{ll}
H_5: & R^{-1}(x) \subseteq S \\
H_6: & R^{-1}_S(x) \subseteq R^{-1}(x) 
\end{array}
\end{fmathpar}
which trivially yields $G_1$ and the proof is completed.\\
\fcolorbox{red}{white}{\color{black} \footnotesize QED.}
\vspace{2mm}
\hrule
\end{proof}
\label {lemma1}
\end{footnotesize}
\input{Sections/minimality_proof}

