\begin{abstract}

  Modern-day distributed systems often use replication to improve
  communication latency and fault tolerance among geographically
  distributed servers and clients.  But, replication compromises
  simplicity because it forces applications to weigh the correctness
  benefits of guaranteeing strong consistency against a potentially
  significant cost in performance.  Because not all operations on a
  replicated data type require strongly consistent behavior, however,
  library designers ought be able to direct implementations to provide
  precisely the level of consistency needed, eschewing the costs of
  strong consistency except when absolutely necessary.  Unfortunately,
  implementations typically support only a small set of consistency
  levels.  Consequently, developers must either be content with
  mapping application requirements to a supported consistency level
  that may well enforce stronger guarantees than required, or hand
  weave a specialized protocol that more accurately matches
  application needs.  The former approach sacrifices performance,
  while the latter introduces unwanted complexity.

  In this paper, we describe a lightweight runtime system for weakly
  consistent distributed systems that dynamically customizes a
  consistency protocol based on a declarative axiomatic specification
  that reflects the necessary constraints any correct implementation
  must satisfy.  Our technique generates a provably optimal runtime
  enforcement mechanism that imposes no additional communication or
  blocking overhead beyond what is required to satisfy the
  specification, thus freeing developers from writing bespoke and
  complex consistency protocols without having to sacrifice
  availability and performance by not doing so.

  We demonstrate the applicability of our approach by automatically
  deriving enforcement mechanisms for various well-known weak
  consistency instantiations.  Experimental results show that the
  performance of our automically derived mechanisms is comparable to
  specialized hand-written protocols, providing strong evidence of its
  practical utility.
\end{abstract}
