% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{xspace}
\usepackage{comment}
\usepackage{mathpartir}
\usepackage{wrapfig}
\usepackage[inline]{enumitem}
\usepackage{bussproofs}
\usepackage{bussproofs}
\usepackage{dsfont}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage{listings}
\usepackage{color}
\usepackage{pifont}
\usepackage{amssymb}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
\definecolor{pred}{rgb}{0.9,0,0}
\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}


\usepackage{listings}
\lstset{language=Java,
  showspaces=false,
  showtabs=false,
  breaklines=true,
  showstringspaces=false,
  breakatwhitespace=false,
  commentstyle=\color{pgreen},
  keywordstyle=\color{pblue},
  stringstyle=\color{pred},
  basicstyle=\footnotesize\tt,
  tabsize=2,
  numbers=left,
  numbersep=0pt,
  numberstyle=\tiny\color{mygray},
  moredelim=[il][\textcolor{pgrey}]{$$},
  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
}
\lstset{escapeinside={(*@}{@*)}}



%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format should change 'acmlarge' to
%% 'sigplan,10pt'.

\usepackage{lipsum}  
%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
\captionsetup{compatibility=false}

%
\begin{document}
%
\frontmatter          % for the preliminaries
%
\input{mydefs}
%
\pagestyle{headings}  % switches on printing of running heads
\addtocmark{Hamiltonian Mechanic} % additional mark in the TOC
%
%
\mainmatter              % start of the contributions
%
\title{\tool : Automatic Enforcement of Distributed Consistency Guarantees}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Kia Rahmani\inst{1} \and Gowtham Kaki\inst{1}\and Suresh
Jagannathan\inst{1}}
%
\authorrunning{Kia Rahmani et al.} % abbreviated author list (for running head)
%
%
\institute{Purdue University, West Lafayette IN 47906, USA\\
\email{\{rahmank,gkaki,suresh\}@purdue.edu}\\
%\texttt{http://users/\homedir iekeland/web/welcome.html}
}
\maketitle              % typeset the title of the contribution

\begin{abstract}
\input{Sections/abstract_short}
\keywords{computational geometry, graph theory, Hamilton cycles}
\end{abstract}

%================================ SECTION ONE: Introduction
\input{Sections/intro}
%================================ SECTION TWO: System Model
\input{Sections/section_two}

\begin{comment}
%================================ SECTION THREE: Motivation
\input{Sections/section_three}

%================================ SECTION FOUR: Operational Semantics
\input{Sections/section_four}

%================================ SECTION FIVE: Instrumented Algorithm
\input{Sections/section_five}

%================================ SECTION SIX: Implementation and Evaluation
\input{Sections/section_six}

%================================ SECTION SEVEN: Related Works
\input{Sections/section_seven}

%================================ SECTION EIGHT: Conclusion 
\input{Sections/section_eight}

\input{Sections/section_nine}
\end{comment}

























%
% ---- Bibliography ----
%
\begin{thebibliography}{5}
%
\bibitem {clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. 78, 315--333 (1982)

\bibitem {clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris 287, 1013--1015 (1978)

\bibitem {mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. 72, 28--55 (1988)

\bibitem {tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)

\bibitem {rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. 33, 609--633 (1980)

\end{thebibliography}
\end{document}
